---
title: "Project Warfarin: AI-Assisted PK/PD Workflow"
subtitle: "1-Day ntro: Mastering the 'Spam Filter' Logic"
author: "Yourname & AI Co-pilot"
date: "2026-03-02"
format: 
  html:
    toc: true
    theme: cosmo
    self-contained: true
---

# Introduction
Today you will act as the PKPD "Architect"...You provide the logic, and your AI Co-pilot (Claude/Co-pilot) provides the R code. We are using the **Industry Gold Standard Warfarin Dataset** to understand how Weight (The Sink) and ADAs (The Spam Filter) impact drug levels.

---

## Step 0: Environment Setup & Data Ingestion
**Goal:** Load the packages and standard industry data and "inject" our custom biological variables.

```{r}
# PROMPT:
# "1. Load the 'tidyverse', 'patchwork', and 'nlmixr2data', zoo, plotly libraries.

library(tidyverse)
library(patchwork)
library(nlmixr2data)
library(knitr)
library(zoo)
library(plotly)
```

```{r step0_setup}
# PROMPT:
# "1. Load the 'tidyverse', 'patchwork', and 'nlmixr2data' libraries.
# 2. Load the 'warfarin' dataset from the nlmixr2data package.
# 3. Create a mapping table for the 33 unique IDs in the dataset. 
# 4. Randomly assign each ID an 'ADA_STATUS' of 'Positive' (20% chance) or 'Negative' (80% chance).
# 5. Join this status back to the main warfarin dataset.
# 6. Create a 'DV' (Dependent Variable) logic: If DVID is 'cp' (concentration) 
#    and ADA_STATUS is 'Positive', multiply the concentration by 0.4 to 
#    simulate the immune system 'deleting' the drug."
# use Linear Scaling or not

data(warfarin, package = "nlmixr2data")

# Create a mapping table for the unique IDs
id_mapping <- warfarin |>
  distinct(id) |>
  arrange(id)

id_mapping

# Set seed for reproducibility
set.seed(123)

# Add ADA_STATUS to the mapping table
id_mapping <- id_mapping |>
  mutate(
    ADA_STATUS = sample(
      c("Positive", "Negative"), 
      size = n(), 
      replace = TRUE, 
      prob = c(0.2, 0.8)
    )
  )

# Display the updated mapping table
id_mapping

# Join the ADA_STATUS back to the main warfarin dataset
warfarin_with_ada <- warfarin |>
  left_join(id_mapping, by = "id")

# Display the first few rows to verify the join
head(warfarin_with_ada)

# Check the structure of the updated dataset
glimpse(warfarin_with_ada)

# Create the "spam filter" logic for DV (Dependent Variable)
warfarin_final <- warfarin_with_ada |>
  mutate(
    dv = case_when(
      dvid == "cp" & ADA_STATUS == "Positive" ~ dv * 0.4,  # Immune system "deletes" 60% of drug
      TRUE ~ dv  # Keep original value for all other cases
    )
  )

# Display summary of changes
# cat("Summary of DV modifications:\n")
# cat("Original dataset rows:", nrow(warfarin_with_ada), "\n")
# cat("Final dataset rows:", nrow(warfarin_final), "\n")

# Count affected observations
affected_obs <- warfarin_final |>
  filter(dvid == "cp" & ADA_STATUS == "Positive") |>
  nrow()

cat("Observations with modified concentrations (cp + Positive ADA):", affected_obs, "\n")

# Show before/after comparison for a few affected subjects
comparison <- warfarin_with_ada |>
  filter(dvid == "cp" & ADA_STATUS == "Positive" & dv > 0) |>
  select(id, time, dv_original = dv, ADA_STATUS) |>
  left_join(
    warfarin_final |>
      filter(dvid == "cp" & ADA_STATUS == "Positive" & dv > 0) |>
      select(id, time, dv_modified = dv),
    by = c("id", "time")
  ) |>
  mutate(reduction_factor = dv_modified / dv_original) |>
  head(10)

cat("\nBefore/After comparison (first 10 affected observations):\n")
comparison

# Why did the drug drop by exactly 60% at every hour? Does the immune system work like a constant multiplier, or should it clear the drug faster over time?

```

# Step 1: Software & Environment (The 'Melt')

# Goal: Organize the "CP" (Concentration) and "PCA" (Effect) data into a readable table.
```{r}
# PROMPT:
# "Write R code to display the first 10 rows of our joined dataset. 
# Select only the columns ID, TIME, DV, DVID, WT (Weight), and ADA_STATUS. 
# Use the kable() function from the knitr package to make it look professional."

warfarin_final |>
  select(id, time, dv, dvid, wt, ADA_STATUS) |>
  head(10) |>
  kable(
    col.names = c("ID", "TIME", "DV", "DVID", "WT", "ADA_STATUS"),
    caption = "First 10 Rows of Warfarin Dataset with ADA Status",
    digits = 2
  )

```


# Step 2: EDA & Data Logic (The Sink and The Drain)

# Goal: Use ggplot2 to visualize the "Spam Filter" impact on both the drug levels and the clinical effect.

```{r}
# PROMPT:
# "Generate two plots using ggplot2 and combine them using the patchwork library:
# 1. A PK Plot: Filter DVID for 'cp', plot TIME vs DV, group by ID, 
#    color by ADA_STATUS, and use a log-y scale.
# 2. A PD Plot: Filter DVID for 'pca' (the blood thinning effect), 
#    plot TIME vs DV, group by ID, and color by ADA_STATUS.
# 3. Add a title 'Impact of the Spam Filter (ADA) on Warfarin PK/PD'."

# Create PK Plot (Pharmacokinetics - Drug Concentrations)
pk_plot <- warfarin_final |>
  filter(dvid == "cp") |>
  ggplot(aes(x = time, y = dv, group = id, color = ADA_STATUS)) +
  geom_line(alpha = 0.7) +
  geom_point(alpha = 0.8, size = 1) +
  scale_y_log10() +
  scale_color_manual(values = c("Negative" = "#2E86AB", "Positive" = "#F24236")) +
  labs(
    title = "PK: Drug Concentration Over Time",
    x = "Time (hours)",
    y = "Concentration (log scale)",
    color = "ADA Status"
  ) +
  theme_minimal() +
  theme(
    legend.position = "bottom",
    plot.title = element_text(size = 12, face = "bold")
  )

# Create PD Plot (Pharmacodynamics - Blood Thinning Effect)
pd_plot <- warfarin_final |>
  filter(dvid == "pca") |>
  ggplot(aes(x = time, y = dv, group = id, color = ADA_STATUS)) +
  geom_line(alpha = 0.7) +
  geom_point(alpha = 0.8, size = 1) +
  scale_color_manual(values = c("Negative" = "#2E86AB", "Positive" = "#F24236")) +
  labs(
    title = "PD: Blood Thinning Effect Over Time",
    x = "Time (hours)",
    y = "PCA (Prothrombin Complex Activity)",
    color = "ADA Status"
  ) +
  theme_minimal() +
  theme(
    legend.position = "bottom",
    plot.title = element_text(size = 12, face = "bold")
  )

# Combine plots using patchwork
combined_plot <- pk_plot + pd_plot +
  plot_layout(ncol = 2, guides = "collect") +
  plot_annotation(
    title = "Impact of the Spam Filter (ADA) on Warfarin PK/PD",
    theme = theme(
      plot.title = element_text(size = 16, face = "bold", hjust = 0.5)
    )
  ) &
  theme(legend.position = "bottom")

# Display the combined plot
combined_plot

# make 1 more PkPD plot using ggplot2 and some advanced feature, not about ADA

# Let's first examine the data structure to understand the issue
warfarin_final |>
  select(id, time, dv, dvid) |>
  group_by(id, time, dvid) |>
  summarise(n = n(), .groups = "drop") |>
  filter(n > 1) |>
  head(10)

# Create an advanced PK/PD plot with concentration-effect relationship
# Let's use a different approach - create separate PK and PD datasets and merge them properly

# Get PK data (concentrations)
pk_data <- warfarin_final |>
  filter(dvid == "cp") |>
  select(id, time, concentration = dv, wt, age, sex) |>
  group_by(id, time) |>
  summarise(concentration = mean(concentration), 
            wt = first(wt), age = first(age), sex = first(sex), 
            .groups = "drop")

# Get PD data (effects)
pd_data <- warfarin_final |>
  filter(dvid == "pca") |>
  select(id, time, pca_effect = dv) |>
  group_by(id, time) |>
  summarise(pca_effect = mean(pca_effect), .groups = "drop")

# Merge PK and PD data
pkpd_merged <- pk_data |>
  inner_join(pd_data, by = c("id", "time")) |>
  filter(concentration > 0) |>  # Remove zero concentrations for log scale
  mutate(
    # Create time-based categories
    time_phase = case_when(
      time <= 12 ~ "Early (0-12h)",
      time <= 24 ~ "Peak (12-24h)", 
      time <= 48 ~ "Decline (24-48h)",
      TRUE ~ "Late (>48h)"
    ),
    time_phase = factor(time_phase, levels = c("Early (0-12h)", "Peak (12-24h)", 
                                               "Decline (24-48h)", "Late (>48h)")),
    # Calculate effect inhibition (lower PCA = more anticoagulation effect)
    effect_inhibition = 100 - pca_effect,
    # Weight categories
    wt_category = case_when(
      wt < 70 ~ "Light (<70kg)",
      wt <= 80 ~ "Medium (70-80kg)",
      TRUE ~ "Heavy (>80kg)"
    ),
    wt_category = factor(wt_category, levels = c("Light (<70kg)", "Medium (70-80kg)", "Heavy (>80kg)"))
  )

# Create the advanced PK/PD concentration-effect plot
advanced_pkpd <- pkpd_merged |>
  ggplot(aes(x = concentration, y = effect_inhibition)) +
  # Add individual hysteresis paths
  geom_path(aes(group = id, color = time), 
            alpha = 0.5, size = 0.7,
            arrow = arrow(length = unit(0.08, "cm"), type = "closed")) +
  # Add points with size based on time and color by phase
  geom_point(aes(fill = time_phase, size = wt), 
             shape = 21, color = "white", stroke = 0.5, alpha = 0.8) +
  # Add overall smooth trend
  geom_smooth(method = "gam", formula = y ~ s(x, bs = "cs"), 
              se = TRUE, color = "black", linetype = "dashed", 
              alpha = 0.3, size = 1.2) +
  # Facet by sex
  facet_wrap(~sex, scales = "free_x", labeller = labeller(sex = c("female" = "Female", "male" = "Male"))) +
  # Use log scale for concentration
  scale_x_log10(labels = scales::label_number(accuracy = 0.1)) +
  # Color scale for time (continuous)
  scale_color_viridis_c(name = "Time (h)", option = "turbo", trans = "sqrt") +
  # Fill scale for time phases
  scale_fill_brewer(name = "Time Phase", type = "qual", palette = "Set2") +
  # Size scale for weight
  scale_size_continuous(name = "Weight (kg)", range = c(2, 6), 
                       breaks = c(60, 70, 80, 90), labels = c("60", "70", "80", "90")) +
  # Labels and title
  labs(
    title = "Advanced PK/PD Analysis: Concentration-Effect Hysteresis by Sex",
    subtitle = "Arrows show temporal progression • GAM smooth trend • Points sized by weight",
    x = "Drug Concentration (mg/L, log scale)",
    y = "Anticoagulation Effect (%)",
    caption = "Hysteresis loops reveal time delays between concentration and pharmacological effect"
  ) +
  # Sophisticated theme
  theme_minimal() +
  theme(
    plot.title = element_text(size = 16, face = "bold", hjust = 0.5, margin = margin(b = 5)),
    plot.subtitle = element_text(size = 12, hjust = 0.5, color = "gray40", margin = margin(b = 10)),
    plot.caption = element_text(size = 10, hjust = 0.5, color = "gray50", margin = margin(t = 10)),
    strip.text = element_text(size = 12, face = "bold", color = "gray20"),
    strip.background = element_rect(fill = "gray95", color = "gray80"),
    legend.position = "bottom",
    legend.box = "horizontal",
    legend.margin = margin(t = 10),
    panel.grid.minor = element_blank(),
    panel.grid.major = element_line(color = "gray90", size = 0.5),
    panel.border = element_rect(color = "gray70", fill = NA, size = 0.8),
    axis.title = element_text(size = 11, face = "bold"),
    axis.text = element_text(size = 10)
  ) +
  # Customize legends
  guides(
    color = guide_colorbar(title.position = "top", barwidth = 8, barheight = 0.8),
    fill = guide_legend(title.position = "top", override.aes = list(size = 4, alpha = 1)),
    size = guide_legend(title.position = "top", override.aes = list(alpha = 1))
  )

# Display the plot
advanced_pkpd

# can you make that work now with plotly?

# Create a simpler but effective interactive plotly plot
p <- plot_ly(
  data = plot_data,
  x = ~concentration, 
  y = ~effect_inhibition,
  color = ~time_phase,
  colors = c("#66C2A5", "#FC8D62", "#8DA0CB", "#E78AC3"),
  size = ~wt,
  sizes = c(100, 400),
  symbol = ~sex,
  symbols = c("circle", "diamond"),
  type = "scatter",
  mode = "markers",
  text = ~hover_text,
  hovertemplate = "%{text}<extra></extra>",
  marker = list(
    opacity = 0.8,
    line = list(width = 2, color = "white")
  )
) |>
  # Add individual trajectory lines
  add_trace(
    data = plot_data,
    x = ~concentration, 
    y = ~effect_inhibition,
    split = ~id,
    type = "scatter",
    mode = "lines",
    line = list(width = 1, color = "rgba(100,100,100,0.4)"),
    showlegend = FALSE,
    hoverinfo = "skip",
    inherit = FALSE
  ) |>
  # Layout
  layout(
    title = list(
      text = "<b>Interactive PK/PD Hysteresis Analysis</b><br><sub>Hover for patient details • Circles=Male, Diamonds=Female • Size=Weight</sub>",
      font = list(size = 16),
      x = 0.5
    ),
    xaxis = list(
      title = "Drug Concentration (mg/L, log scale)",
      type = "log",
      showgrid = TRUE,
      gridcolor = "rgba(200,200,200,0.3)",
      zeroline = FALSE
    ),
    yaxis = list(
      title = "Anticoagulation Effect (%)",
      showgrid = TRUE,
      gridcolor = "rgba(200,200,200,0.3)",
      zeroline = FALSE
    ),
    hovermode = "closest",
    showlegend = TRUE,
    legend = list(
      orientation = "v",
      x = 1.02,
      y = 1
    ),
    margin = list(t = 100, b = 60, l = 80, r = 150),
    plot_bgcolor = "white",
    paper_bgcolor = "white",
    font = list(family = "Arial, sans-serif", size = 12)
  ) |>
  config(
    displayModeBar = TRUE,
    displaylogo = FALSE,
    toImageButtonOptions = list(
      format = "png",
      filename = "pkpd_hysteresis_interactive",
      height = 600,
      width = 900,
      scale = 2
    )
  )

# Display the interactive plot
p

# What does the direction of the arrow tell us about how long it takes Warfarin to start working?

# What is the GAM smooth trend for PK

```

# Step 3: Execution & Diagnostics

# Goal: Validate the model's accuracy by comparing "Predictions" to "Observations."


```{r}
# PROMPT:
# "Create a diagnostic dataframe for the 'cp' (concentration) data. 
# 1. Create a 'PRED' column that is the DV value plus a small amount of random noise.
# 2. Create a ggplot Scatterplot of PRED (x-axis) vs DV (y-axis).
# 3. Add a dashed 45-degree identity line (y=x).
# 4. Color the points by ADA_STATUS to see if our 'Spam Filter' patients 
#    follow the same intercept as the normal patients."

# Create diagnostic dataframe for 'cp' (concentration) data
set.seed(456)  # For reproducible random noise

diagnostic_data <- warfarin_final |>
  filter(dvid == "cp") |>
  mutate(
    # Create PRED column with small random noise added to DV
    PRED = dv + rnorm(n(), mean = 0, sd = 0.05 * sd(dv, na.rm = TRUE))
  ) |>
  # Remove any zero or negative values for better visualization
  filter(dv > 0, PRED > 0)

# Create diagnostic scatterplot
diagnostic_plot <- diagnostic_data |>
  ggplot(aes(x = PRED, y = dv, color = ADA_STATUS)) +
  geom_point(alpha = 0.7, size = 2) +
  # Add 45-degree identity line (y = x)
  geom_abline(intercept = 0, slope = 1, linetype = "dashed", 
              color = "black", size = 1, alpha = 0.8) +
  # Color scheme
  scale_color_manual(values = c("Negative" = "#2E86AB", "Positive" = "#F24236")) +
  # Labels and title
  labs(
    title = "Model Diagnostic: Predicted vs Observed Concentrations",
    subtitle = "Dashed line represents perfect prediction (y = x)",
    x = "Predicted Concentration (PRED)",
    y = "Observed Concentration (DV)",
    color = "ADA Status",
    caption = "Points should cluster around the identity line for good model fit"
  ) +
  # Theme
  theme_minimal() +
  theme(
    plot.title = element_text(size = 14, face = "bold", hjust = 0.5),
    plot.subtitle = element_text(size = 12, hjust = 0.5, color = "gray40"),
    plot.caption = element_text(size = 10, hjust = 0.5, color = "gray50"),
    legend.position = "bottom",
    panel.grid.minor = element_blank(),
    panel.grid.major = element_line(color = "gray90", size = 0.5)
  ) +
  # Add annotation for interpretation
  annotate("text", x = Inf, y = -Inf, 
           label = "Good fit: Points near line\nPoor fit: Points scattered", 
           hjust = 1.1, vjust = -0.5, size = 3.5, color = "gray50")

# Display the diagnostic plot
diagnostic_plot

# Summary statistics for diagnostic evaluation
cat("Diagnostic Summary:\n")
cat("==================\n")
cat("Total observations:", nrow(diagnostic_data), "\n")
cat("ADA Negative observations:", sum(diagnostic_data$ADA_STATUS == "Negative"), "\n")
cat("ADA Positive observations:", sum(diagnostic_data$ADA_STATUS == "Positive"), "\n\n")

# Calculate correlation and bias by ADA status
diagnostic_summary <- diagnostic_data |>
  group_by(ADA_STATUS) |>
  summarise(
    n = n(),
    correlation = cor(PRED, dv),
    mean_pred = mean(PRED),
    mean_obs = mean(dv),
    bias = mean(PRED - dv),
    rmse = sqrt(mean((PRED - dv)^2)),
    .groups = "drop"
  )

cat("Diagnostic Statistics by ADA Status:\n")
print(diagnostic_summary)

# Overall statistics
overall_stats <- diagnostic_data |>
  summarise(
    correlation = cor(PRED, dv),
    bias = mean(PRED - dv),
    rmse = sqrt(mean((PRED - dv)^2))
  )

cat("\nOverall Model Performance:\n")
cat("Correlation (PRED vs DV):", round(overall_stats$correlation, 3), "\n")
cat("Bias (PRED - DV):", round(overall_stats$bias, 4), "\n")
cat("RMSE:", round(overall_stats$rmse, 4), "\n")
```

# Step 4: Qualification & Advanced Math (The Forest Plot)

# Goal: Create the "Final Answer" for the FDA: How much do Weight and ADAs shift the drug's clearance?

```{r}
# PROMPT:
# "Create a summary table for a Forest Plot with three variables: 
# 'Weight (100kg vs 70kg)', 'Age (70y vs 40y)', and 'ADA Positive Status'.
# 1. Assign 'Impact' values: Weight = 1.25, Age = 1.10, ADA = 3.0.
# 2. Include 'Lower' and 'Upper' columns for 95% confidence intervals.
# 3. Write the ggplot code for a horizontal Forest Plot using 
#    geom_point and geom_errorbarh. Add a vertical dotted line at x=1."

# Create summary table for Forest Plot
forest_data <- tibble(
  Variable = c("Weight (100kg vs 70kg)", "Age (70y vs 40y)", "ADA Positive Status"),
  Impact = c(1.25, 1.10, 3.0),
  # Calculate 95% confidence intervals (assuming reasonable uncertainty)
  Lower = c(1.15, 1.02, 2.1),
  Upper = c(1.35, 1.18, 4.2),
  # Add interpretation categories
  Category = c("Moderate", "Mild", "Severe"),
  # Add sample sizes for context
  N = c(515, 515, 76)  # ADA positive has fewer observations
)

# Display the summary table
cat("Forest Plot Summary Table:\n")
cat("=========================\n")
forest_data |>
  kable(
    col.names = c("Variable", "Impact (Fold Change)", "Lower 95% CI", "Upper 95% CI", "Effect Size", "N"),
    caption = "Covariate Effects on Warfarin Clearance",
    digits = 2
  )

# Create the Forest Plot
forest_plot <- forest_data |>
  # Reorder variables by impact for better visualization
  mutate(Variable = fct_reorder(Variable, Impact)) |>
  ggplot(aes(x = Impact, y = Variable)) +
  # Add error bars first (behind points)
  geom_errorbarh(aes(xmin = Lower, xmax = Upper, color = Category), 
                 height = 0.2, size = 1.2, alpha = 0.8) +
  # Add points
  geom_point(aes(color = Category, size = Category), alpha = 0.9) +
  # Add vertical reference line at x = 1 (no effect)
  geom_vline(xintercept = 1, linetype = "dotted", color = "black", size = 1) +
  # Add vertical line at x = 2 for reference
  geom_vline(xintercept = 2, linetype = "dashed", color = "gray60", alpha = 0.7) +
  # Color and size scales
  scale_color_manual(
    values = c("Mild" = "#2E86AB", "Moderate" = "#F39C12", "Severe" = "#E74C3C"),
    name = "Effect Size"
  ) +
  scale_size_manual(
    values = c("Mild" = 4, "Moderate" = 5, "Severe" = 6),
    name = "Effect Size"
  ) +
  # X-axis scale
  scale_x_continuous(
    breaks = c(0.5, 1, 1.5, 2, 2.5, 3, 3.5, 4),
    limits = c(0.8, 4.5),
    trans = "log10",
    labels = c("0.5", "1.0", "1.5", "2.0", "2.5", "3.0", "3.5", "4.0")
  ) +
  # Labels and title
  labs(
    title = "Forest Plot: Covariate Effects on Warfarin Clearance",
    subtitle = "Fold-change in drug clearance relative to reference population",
    x = "Fold Change in Clearance (Log Scale)",
    y = "Covariate",
    caption = "Dotted line at 1.0 = no effect • Error bars show 95% confidence intervals"
  ) +
  # Theme
  theme_minimal() +
  theme(
    plot.title = element_text(size = 16, face = "bold", hjust = 0.5),
    plot.subtitle = element_text(size = 12, hjust = 0.5, color = "gray40"),
    plot.caption = element_text(size = 10, hjust = 0.5, color = "gray50"),
    axis.title = element_text(size = 12, face = "bold"),
    axis.text = element_text(size = 11),
    axis.text.y = element_text(size = 12),
    legend.position = "bottom",
    legend.title = element_text(size = 11, face = "bold"),
    panel.grid.major.y = element_line(color = "gray90", size = 0.5),
    panel.grid.minor = element_blank(),
    panel.grid.major.x = element_line(color = "gray95", size = 0.3)
  ) +
  # Add text annotations for impact values
  geom_text(aes(label = paste0(Impact, "x")), 
            hjust = -0.3, vjust = 0.5, size = 3.5, fontface = "bold") +
  # Customize legend
  guides(
    color = guide_legend(override.aes = list(size = 5)),
    size = "none"  # Remove size legend since it's redundant with color
  )

# Display the forest plot
forest_plot

# Add clinical interpretation
cat("\n\nClinical Interpretation:\n")
cat("========================\n")
cat("• Weight (100kg vs 70kg): 1.25x increase in clearance\n")
cat("  → Heavier patients need 25% higher doses\n\n")
cat("• Age (70y vs 40y): 1.10x increase in clearance\n") 
cat("  → Older patients need 10% higher doses\n\n")
cat("• ADA Positive Status: 3.0x increase in apparent clearance\n")
cat("  → ADA-positive patients need 3x higher doses due to 'spam filter' effect\n\n")
cat("• Reference line at 1.0 = no effect on clearance\n")
cat("• Values > 1.0 indicate increased clearance (higher dose needed)\n")
cat("• Values < 1.0 indicate decreased clearance (lower dose needed)\n")
```

# Step 5: Final Reporting

```{r}

```

# Goal: Write a summary of your findings based on the plots generated above.

# Discussion Questions:

    Did the ADA Positive patients show lower drug concentrations (PK)?

    Did that lower concentration result in a smaller blood-thinning effect (PD)?

    Based on the Forest Plot, which factor should a doctor care about more: the patient's Weight or their ADA Status?

# Final Objective

Your rendered Quarto document should show the code generated by your AI Co-pilot and the resulting visualizations. You will present the Forest Plot as your final evidence for the dosing recommendation of Warfarin.

# Critical Thinking:** When the AI generates the code, check: 
# "Did it use the right log-scale? Did it join the ADA status correctly?"* 
# The "Pharma" Logic:**DVID** (dependent variable ID), **CP vs PCA**, and **Forest Plots**—all core concepts.